---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Overview

mypackage is a simple tool to perform linear model fitting and can achieve efficient simple analysis. It has one main function `myLm()`. The purpose of this vignette is to demonstrate some usage examples of `myLm()` based on the data set `USArrests`, and do some benchmark against the built-in r function `lm()`

## Requirements

To get started, you will need to install and load a few packages:

```{r setup}
library(mypackage)
library(bench)
```


## Example Usage for function `myLm()`

From the below demonstration we can see that `myLm()` produces the same result as `lm()` does

**Result from `myLm()`**
```{r}

m1 = myLm(Murder~Rape, USArrests)

m1$Residuals
m1$df.residual
m1$Ftest
m1$F.statistic
m1$residuals
m1$Multiple.Rsquared
m1$Adjusted.Rsquared

```

```{r}
m1$Coefficients

```

**Result from `summary(lm())`**

```{r}
lm(Murder~Rape, USArrests)$residuals
summary(lm(Murder~Rape, USArrests))
```



## How does it compare with lm( )? 

First let's build two models using lm() and myLm() respectively

```{r, fig.align ='center', fig.width= 6, fig.height = 3}
m1_bylm = lm(formula = Murder~Rape+Assault, data = USArrests)

m2_bymyLm = myLm(formula = Murder~Rape+Assault,data = USArrests)

```


**Comparing Performance on Obtaining Residuals**

```{r, fig.align ='center', fig.width= 6, fig.height = 3}
benchmark = bench::mark(m1_bylm$residuals, m2_bymyLm$residuals)
print(benchmark)
ggplot2::autoplot(benchmark)
```


**Comparing Performance on Obtaining coefficients**

```{r, fig.align ='center', fig.width= 6, fig.height = 3}
benchmark = bench::mark(as.matrix(summary(m1_bylm)$coefficients),
                        as.matrix(m2_bymyLm$Coefficients))
print(benchmark)
ggplot2::autoplot(benchmark)
```



**Comparing Performance on Obtaining fitted.values**


```{r, fig.align ='center', fig.width= 6, fig.height = 3}
benchmark = bench::mark(m1_bylm$fitted.values, m2_bymyLm$fitted.values)
print(benchmark)
ggplot2::autoplot(benchmark)
```


The above three plots clearly shows that `myLm()` outperforms `lm( )` in cases dealing with simple analysis. 



